### 2020-06-01 README.Rmd
readme update :pen:

The goal of neonstore is to provide access and persistent storage of NEON data tables.

@@

``` r
# install.packages("devtools")
devtools::install_github("cboettig/neonstore")
```
## Example

Download all CSV files in the bird survey data products.  This will omit downloads of any existing data files.

```{r example, cache=TRUE}
library(neonstore)
neon_download("DP1.10003.001", file_regex = "[.]csv")

@@

Now, view your library of NEON products.  These will persist between sessions, 
so you only need to download once, or to retrieve updates.

```{r }
neon_tables()
```
See files associated with a given table,

```{r}
meta <- neon_index("brd_countdata") 
meta
```

@@

```{r message = FALSE}
brd_countdata <- neon_read(meta)
brd_countdata
```

>>>>

The goal of neonstore is to provide quick access and persistent storage of NEON data tables.

@@

``` r
# install.packages("devtools")
devtools::install_github("cboettig/neonstore")
```
## Quickstart

Discover data products of interest:

```{r}
products <- neon_products()

i <- grepl("Populations", products$themes)
products[i, c("productCode", "productName")]

i <- grepl("bird", products$keywords)
products[i, c("productCode", "productName")]
```

Download all data files in the bird survey data products.

```{r example, cache=TRUE}
library(neonstore)
neon_download("DP1.10003.001")

@@

Now, view your store of NEON products.  These will persist between sessions,
so you only need to download once, or to retrieve updates.
(Note: the individual files making up a data product can all be listed by
`neon_index()`).

```{r }
neon_store()
```

@@

```{r}
neon_read("brd_countdata")
```

## Details

`neon_download()` will omit downloads of any existing data files. 
You can request multiple products at once using vector notation. 
You can optionally include date filters, e.g. to request only records more recent
than a certain date. 
Doing so will preserve API quota and improve speed (see API limits, below).

Because `neonstore` only stores raw data products as returned from the NEON API,
this makes it easy to track provenance and compare results across other analyses
of the NEON data.

## Note on API limits

[The NEON API now rate-limits requests.](https://data.neonscience.org/data-api/rate-limiting/#api-tokens).
Using a personal token will increase the number of requests you can make.
See that link for directions on registering for a token.
Then pass this token in `.token` argument of `neon_download()`,
or for frequent use, add this token as  an environmental variable, `NEON_DATA`
to your local `.Renviron` file in your user's home directory.

`neon_download()` must first query each the API of eacn NEON site which collects
that product, for each month the product is collected.  
(It would be much more efficient on the NEON server if the API could take
queries of the from `/data/<product>/<site>, and pool the results, rather than
require each month of sampling separately!)
